---
title: "Exercises: 05-20-20"
author: "Shawn Santo"
date: ""
output: 
  html_document:
    css: "exercises.css"
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: false
    df_print: paged
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

# Slide Example, Video 1
```{r slide-vid1}
df <- data.frame(coin = c("BTC", "ETH", "XRP"),
 price = c(10417.04, 172.52, .26),
 vol = c(21.29, 8.07, 1.23),
 stringsAsFactors = FALSE)

#df[1]
#df[c(1, 3)]
#df[1:2, 3]
#df[, "price"]

#df[[1]]
#df[["vol"]]
#df[[c(1, 3)]]
#df[[1, 3]]
```


# Exercise 1 {.tabset .tabset-fade .tabset-pills}

## Problem

Use the built-in data frame `longley` to answer the following questions.

1. What year was the percentage of people employed relative to the population
   highest? Return the result as a data frame.
   
```{r p1-att}
longley

longley[which.max(longley$Employed / longley$Population), 
        "Year", drop=FALSE]
```

   
2. The Korean war took place from 1950 - 1953. Filter the data frame so it only
   contains data from those years.
  
  
```{r p2-att}
longley[longley$Year %in% 1950:1953, ]

```

3. What years did the number of people in the armed forces exceed the number
   of people unemployed? Give the result as an atomic vector.

```{r p3-att}
longley$Year[longley$Armed.Forces > longley$Unemployed]
```

## Solution

#### Part 1

```{r}
longley[which.max(longley$Employed / longley$Population), 
        "Year", drop=FALSE]
```

#### Part 2

```{r}
longley[longley$Year %in% 1950:1953, ]
```

#### Part 3

```{r}
longley$Year[longley$Armed.Forces > longley$Unemployed]
```

# Exercise 2 {.tabset .tabset-fade .tabset-pills}

## Problem

1. Use function `sloop::ftype()` to see which of the following functions are
   S3 generics: `mean`, `summary`, `print`, `sum`, `plot`, `View`, `length`, 
   `[`.
```{r ex2-p1}
sloop::is_s3_generic("mean")
sloop::is_s3_generic("summary")
sloop::is_s3_generic("print")
sloop::is_s3_generic("sum")
sloop::is_s3_generic("plot")
sloop::is_s3_generic("View")
sloop::is_s3_generic("length")
sloop::is_s3_generic("[")

```



2. Choose 2 of the S3 generics you identified above. How many methods exist for
   each? Use function `sloop::s3_methods_generic()`.
   
```{r ex2-p2}
sloop::s3_methods_generic("mean")
sloop::s3_methods_generic("summary")
```   
3. How many methods exist for classes `factor` and `data.frame`. 
   Use function `sloop::s3_methods_class()`.
 
 
```{r ex2-p3}
sloop::s3_methods_class("factor")
sloop::s3_methods_class("data.frame")
```

4. Consider a class called dollars. If a numeric vector has class dollars,
   function `print()` should print the vector with a $ in front of each number
   and round digits to two decimals.
   
   
```{r ex2-p4}

```

## Solution

#### Part 1

```{r}
library(sloop)
```

Checking a couple of the functions:

```{r}
ftype(mean)
ftype(plot)
```

#### Part 2

```{r}
nrow(s3_methods_generic("mean"))
nrow(s3_methods_generic("plot"))
```

#### Part 3

```{r}
nrow(s3_methods_class("factor"))
nrow(s3_methods_class("data.frame"))
```

#### Part 4

```{r}
print.dollar <- function(x) {
  paste0("$", round(x, digits = 2))
}
```

```{r}
x <- 1:5
class(x) <- "dollar"
print(x)
```

```{r}
y <- c(4.292, 134.1133, 50.111)
class(y) <- "dollar"
print(y)
```